\documentclass[10pt,letter]{article}
\usepackage{fontspec,tikz}
\usepackage[margin=1.5in, top=1in, bottom=1in]{geometry}

%% \setmainfont{Avenir Next LT Pro}
\setlength{\parindent}{0pt}
\pagenumbering{gobble}

\definecolor{gold}{rgb}{1,0.9,0.2}
\definecolor{magentared}{rgb}{0.9,0,0.5}
\definecolor{lightblue}{rgb}{0.1,0.7,1}

\begin{document}

\hspace*{-1.1in}
\begin{tikzpicture}[scale=0.6]
  \fill[gold!100] (0,0) rectangle (1,1);
  \fill[magentared!100] (1.2, 0) rectangle (2.2, 1);
  \fill[lightblue!100] (2.4, 0) rectangle (3.4, 1);
\end{tikzpicture}

\vspace*{-0.25in}
\textbf{\Huge Jacob Evan Shreve}

\vspace{0.25in}

{517.518.2358 \hspace{0.3in} jacob@shreve.io \hspace{0.3in} shreve.io \hspace{0.3in} github.com/shreve}
\vspace{0.25in}

\textit{\large{
An ambitious, adaptable learner with five years of real-world tech industry experience
collaborating in small teams to get things done.
}}
\vspace{0.25in}

\vspace{0.15in}
{\Large\textbf{Experience}}
\vspace{0.15in}

\textbf{Product Lead, Wellopp; Toledo, OH --- Jan 2016-Present} \\
Wellopp is dedicated to reducing uneccessary hospital readmissions. At Wellopp, I lead
the development of our messenger product, an SMS-powered patient outreach tool. I
also held the role of ``swingman'', fixing bugs in other products, as well as helping
the dev ops team administer our microservice architecture.
\vspace{0.25in}

\textbf{Sole Proprietor, I Make Websites, LLC; Ypsilanti, MI --- Aug 2012-Present} \\
I Make Websites is the company I created for my freelance programming work. This
encapsulates all of my experience working solo to meet with clients, discuss project goals,
develop timelines, and get things done.
\vspace{0.25in}

\textbf{Web Developer, Online Ventures; Brighton, MI --- Apr 2012-May 2014} \\
Online Ventures is a technology consultancy that focuses on delivering quality results that
improve clients’ business performance. During my time there, I worked on several large
projects targeted toward making the operations of non-profit organizations easier,
especially datekeeper.org, an event management system targeted toward non-profits.
\vspace{0.25in}

\vspace{0.15in}
{\Large\textbf{Education}}
\vspace{0.15in}

\textbf{University of Michigan, Ann Arbor --- Fall 2016-Present} \\
Bachelor's in Computer Science in Engineering, Minor in Political Science \\
Data structures, algorithms, discrete math

\vspace{0.25in}

\textbf{Washtenaw Community College, Ann Arbor --- Fall 2013-Winter 2016} \\
Engineering prerequisites, including Calculus 1-4, Linear Algebra, Chemistry, and Physics

\vspace{0.25in}

\vspace{0.15in}
{\Large\textbf{Skills}}

\begin{itemize}
  \item{Strong team communication and collaboration skills}
  \item{Proficiency in Ruby, JavaScript, Elixir, C/C++, SQL, HTML/CSS}
  \item{Linux server management, including web app and email servers}
  \item{Containerized app cluster management using Kubernetes}
  \item{Git and Mercurial version control systems}
\end{itemize}

\end{document}
