\documentclass[10pt]{article}
\usepackage{fontspec,tikz}
\usepackage[letterpaper, margin=1in, top=0.5in, bottom=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{textpos}
\usepackage{xhfill}
\usepackage[hidelinks]{hyperref}
\usepackage[none]{hyphenat}

\hypersetup{
  bookmarks = true,
  colorlinks = false,
  pdftitle = {Jacob Evan Shreve -- Software Engineer Candidate},
  pdfpagemode = FullScreen
}
\urlstyle{same}

\setlength{\parindent}{0pt}
\pagenumbering{gobble}

\definecolor{gold}{rgb}{1,0.9,0.2}
\definecolor{magentared}{rgb}{0.9,0,0.5}
\definecolor{lightblue}{rgb}{0.1,0.7,1}
\definecolor{grey}{rgb}{0.6,0.6,0.6}

\newcommand{\invisible}[1]{
  \begin{textblock}{100} (0,0)
    \textcolor{white}{#1}
  \end{textblock}
}

\newcommand \fullname {Jacob Evan Shreve}
\newcommand \user {shreve}
\newcommand \phone {517.518.2358}

\newcommand{\dummymode}{
  \renewcommand \fullname {Jacob Smith}
  \renewcommand \user {smith}
  \renewcommand \phone {555.867.5309}
}

\newcommand{\sectiontitle}[1]{
  %                    lift,   width, weight
  {\color{grey}\rule[0.15cm]{0.5cm}{0.5pt}}
  {\Large\textbf{#1}}
  %         lift,  weight
  \xrfill[0.1cm]{0.5pt}[grey]
}

\newcommand{\itempad}{\vspace{0.1in}}

  \begin{document}

  \invisible{https://shreve.io}

  %% width, x, y
  \begin{textblock}{0}(10.3,0.0)
    \begin{tikzpicture}[scale=0.65, rotate=90]
      \fill[magentared!100] (0, 0) rectangle (1, 1);
      \fill[lightblue!100] (0, 1.5) rectangle (1, 2.5);
      \fill[gold!100] (0, 3) rectangle (1, 4);
    \end{tikzpicture}
  \end{textblock}

  \textbf{\Huge \fullname}

  \vspace{0.15in}
  {\Large \href{mailto:hire-me@shreve.io}{hire-me@\user.io} \hfill
  \href{https://shreve.io}{\user.io} \hfill
  \href{https://github.com/shreve}{github.com/\user} \hfill
  \phone}\\
  \vspace{0.05in}

  %%
  %% Experience
  %%
  \sectiontitle{Experience}
  \vspace{0.1in}

  \textbf{Research Assistant, \href{https://refraction.network/}{Refraction Networking}, Remote \hfill Summer 2020}\\
  Refraction Networking is a project which develops censorship circumvention tools.
  \vspace{-0.07in}
  \begin{itemize}[leftmargin=1em]
    \setlength\itemsep{-0.3em}
    \item Developed method to resume TLS 1.3 sessions on a proxy server with OpenSSL, C, and Rust.
    \item Updated Tapdance protocol spec and Golang client implementation to reflect TLS 1.3 changes.
    \item References: \href{https://ericw.us/trow/}{Eric Wustrow}, \href{https://www.linkedin.com/in/jack-wampler-24a65190/}{Jack Wampler}, and \href{https://jhalderm.com/}{J. Alex Halderman}
  \end{itemize}
\itempad

  \textbf{Software Engineer, \href{https://wellopp.com/}{Wellopp}, Remote \hfill Jan 2016-Aug 2019}\\
  Wellopp is a healthcare startup dedicated to reducing uneccessary hospital readmissions.
  \vspace{-0.07in}
  \begin{itemize}[leftmargin=1em]
    \setlength\itemsep{-0.3em}
    \item Developed SMS patient outreach product using Twilio API and Ruby on Rails.
    \item Containerized application and created CI/CD pipeline with CircleCI and Kubernetes.
    \item Started a documentation corpus for onboarding, deployment, and maintenance topics.
    \item References: \href{https://www.linkedin.com/in/jon-wiedmann-b6442b67/}{Jon Wiedmann},
      \href{https://www.linkedin.com/in/nicholasgronow/}{Nicholas Gronow},
      and \href{https://www.linkedin.com/in/andrew-stewart-95772914b/}{Andrew Stewart}
  \end{itemize}
\itempad

  \textbf{Freelance Web Developer, Shreve Labs, Remote \hfill Aug 2014-Dec 2015}\\
  Shreve Labs is the company I created for my freelance work and side projects.
  \vspace{-0.07in}
  \begin{itemize}[leftmargin=1em]
    \setlength\itemsep{-0.3em}
    \item Developed and maintained Ruby and Ruby on Rails software for clients around the world.
  \end{itemize}
\itempad

  \textbf{Web Developer, \href{https://www.linkedin.com/company/online-ventures/}{Online Ventures}, Howell, MI \hfill Apr 2012-May 2014}\\
  Online Ventures is a consultancy that improves clients’ business performance with software.
  \vspace{-0.07in}
  \begin{itemize}[leftmargin=1em]
    \setlength\itemsep{-0.3em}
    \item Created specialized CMS software for several local businesses to complement their workflows.
  \end{itemize}
\itempad


  %%
  %% Education
  %%
  \sectiontitle{Education}
  \vspace{0.1in}

  \textbf{\href{https://ro.umich.edu/graduation/diplomas/degree-verification?dvid=C68OH1JS}{B.S.E. in Computer Science} \hfill  Graduated August 2020} \\
  University of Michigan, Ann Arbor
  \vspace{-0.07in}
  \begin{itemize}[leftmargin=1em]
    \setlength\itemsep{-0.3em}
    \item \textit{Course Work: } Cryptography, Computer Security, Computer Architecture, Operating Systems,\\
      Web Systems, Data Structures \& Algorithms, Statistics, Video Game Development, Ethics
    \item Created UI for \href{https://wolverinesoft-studio.itch.io/io}{WolverineSoft Game Dev Club's Semester Studio Project} with over 60 contributors
  \end{itemize}
\itempad

  %%
  %% Projects
  %%
  \sectiontitle{Projects}
  \begin{itemize}[leftmargin=1em]
    \setlength\itemsep{-0.3em}
    \item \textit{MapReduce Server:} Hadoop-style master and worker for distributed computation with Python
    \item \textit{Network File System:} A concurrent, remote over TCP, crash-safe file system interface
    \item \textit{Web Security:} SQL-injection, XSS, and CSRF expoits in CTF challenges
    \item \textit{\href{https://github.com/shreve/go-roku}{Roku}:} Libraries in Go, Ruby, and Rust which find and control Roku devices on the network
    \item \textit{\href{https://github.com/shreve/tui}{tui}:} A Go library for building and efficiently rendering terminal user interface applications
    \item \textit{\href{https://github.com/shreve/sso}{sso}:} Automatic multi-site single sign on library in Go \`{a} la Stack Exchange
    \item \textit{\href{https://github.com/shrve/shared-secret}{Secret Sharing}:} A Ruby library which implements Shamir's Secret Sharing
  \end{itemize}
\itempad

  %%
  %% Skills
  %%
  \sectiontitle{Skills}

  \begin{itemize}[leftmargin=1em]
    \setlength\itemsep{-0.3em}
    \item{Golang, Ruby, Python, C, C++, HTML/CSS/JS, SQL, PHP, Unity3D/C\#. Learning Rust.}
    \item{PostgreSQL, SQLite3 database administration}
    \item{DevOps with Docker and Kubernetes. Experience with GCP, AWS, and Heroku.}
    \item{OS programming: concurrency, memory management, resource contention}
    \item{Networked programming: sockets, TCP/IP, TLS, DNS}
    \item{Mastery of shared version control with Git}
    \item{Debugging: I love finding the source of a bug by searching logs, gdb, or just reading the code}
  \end{itemize}
\end{document}
